---
title: "NewsTLGetter"
output: html_notebook
editor_options: 
  chunk_output_type: console
---
```{r}
library(dplyr); library(tidyr) ; library(rtweet); library(tidytext) ; library(beepr) ## load libraries
```

## 1 NewsTLs
## Authenticate : 
Insert API keys here for each of api_key, api_secret, access_token, access_secret, and bearer_token, then add nape to app
```{r}
{ twitterapp_keylist <- list(
  api_key = "",
  api_secret = "",
  access_token = "",
  access_secret = "",
  bearer_token = ""
)
  my_token1 <- create_token(
    app = "", # the name of my app
    consumer_key = twitterapp_keylist$api_key,
    consumer_secret = twitterapp_keylist$api_secret,
    access_token = twitterapp_keylist$access_token,
    access_secret = twitterapp_keylist$access_secret
  )
}
```



```{r}
TLsV2 <- read.csv("/R/NewsTLs/NewsTLsCodesV2.csv", header = T)
TLsV2$screen_name <- gsub("@", "", TLsV2$Handle)
thisYear <- format(Sys.Date(), "%Y")
YesterdayMonth <- format(Sys.Date(), "%m")
#YesterdayMonth <- as.integer(YesterdayMonth) -1
#YesterdayMonth <-paste("0", YesterdayMonth, sep="") 
#YesterDate <- 30
thisDay <- as.numeric(format(Sys.Date(), "%d"))
if ((thisDay <10)){
  thisDay <- paste(0,thisDay, sep = "")}
YesterDate <- as.numeric(thisDay) -1
if ((YesterDate <10)){
  YesterDate <- paste(0,YesterDate, sep = "")}
YesterdayYMDString <- paste(thisYear, YesterdayMonth, YesterDate, sep="-")
DailyPath <-  paste("/R/NewsTMLS/Archive/Dailies/", thisYear, "/", YesterdayYMDString, sep="")
#ifelse( !dir.exists(file.path(DailyPath)),   dir.create(file.path(DailyPath)),   FALSE  )

```

## Get 
```{r}
{
currentOutput <- data.frame()
for (i in 1:9){
  currentFeed <- get_timeline(TLsV2$Handle[i], n = 1000, token = my_token1)
  currentFeed <- currentFeed[-c(1,6:10,13:90)]
  allCurrentInfo <- right_join(currentFeed, TLsV2, by = "screen_name") %>% 
      na.omit(text) 
  allCurrentInfo<- allCurrentInfo[-c(7,8,10)]  
  allCurrentInfo <- allCurrentInfo[which(allCurrentInfo$is_quote == F),] ## get rid of quotes and retweets
  allCurrentInfo <- allCurrentInfo[which(allCurrentInfo$is_retweet == F),]
  allCurrentInfo <- allCurrentInfo[-c(5,6)]
  allCurrentInfo <- unique.data.frame(allCurrentInfo)
  currentOutput <- rbind(currentOutput, allCurrentInfo)
  cat ("Completed", i, TLsV2$Handle[i], ";", dim(allCurrentInfo)[1], "added", "total :", dim(currentOutput)[1], "\n")
}
{
BE_TML <- currentOutput
BE_TML <- separate(BE_TML, created_at, c("Date", "Time"), sep= " ")
BE_TML <- separate(BE_TML, Date, c("YYYY", "MM", "DD"), sep= "-")
BE_TML <- separate(BE_TML, Time, c("hh", "mm", "ss"), sep= ":")
BE_TML <- BE_TML[which(BE_TML$YYYY == thisYear), ]
BE_TML <- BE_TML[which(BE_TML$MM == YesterdayMonth), ]
BE_TML <- BE_TML[which(BE_TML$DD == YesterDate), ]
BE_TML <- unique.data.frame(BE_TML)
write.csv(BE_TML, paste(DailyPath, "-BE_TML.csv", sep=""))
#write.csv(BE_TML, paste("/R/NewsTMLS/", YesterdayYMDString, "-BE_TML.csv", sep=""))

}
}
{
currentOutput <- data.frame()
for (i in 10:34){
  currentFeed <- get_timeline(TLsV2$Handle[i], n = 1000, token = my_token1)
  currentFeed <- currentFeed[-c(1,6:10,13:90)]
  allCurrentInfo <- right_join(currentFeed, TLsV2, by = "screen_name") %>% 
      na.omit(text) 
  allCurrentInfo<- allCurrentInfo[-c(7,8,10)]  
  allCurrentInfo <- allCurrentInfo[which(allCurrentInfo$is_quote == F),] ## get rid of quotes and retweets
  allCurrentInfo <- allCurrentInfo[which(allCurrentInfo$is_retweet == F),]
  allCurrentInfo <- allCurrentInfo[-c(5,6)]
  allCurrentInfo <- unique.data.frame(allCurrentInfo)
  currentOutput <- rbind(currentOutput, allCurrentInfo)
  cat ("Completed", i,  TLsV2$Handle[i], ";", dim(allCurrentInfo)[1], "added", "total :", dim(currentOutput)[1], "\n" )
}
{
CA_TML <- currentOutput
CA_TML <- separate(CA_TML, created_at, c("Date", "Time"), sep= " ")
CA_TML <- separate(CA_TML, Date, c("YYYY", "MM", "DD"), sep= "-")
CA_TML <- separate(CA_TML, Time, c("hh", "mm", "ss"), sep= ":")
CA_TML <- CA_TML[which(CA_TML$YYYY == thisYear), ]
CA_TML <- CA_TML[which(CA_TML$MM == YesterdayMonth), ]
CA_TML <- CA_TML[which(CA_TML$DD == YesterDate), ]
CA_TML <- unique.data.frame(CA_TML)
write.csv(CA_TML, paste(DailyPath, "-CA_TML.csv", sep=""))
#write.csv(CA_TML, paste("/R/NewsTMLS/", YesterdayYMDString, "-CA_TML.csv", sep=""))
}
}
{
currentOutput <- data.frame()
for (i in 35:53){
  currentFeed <- get_timeline(TLsV2$Handle[i], n = 1000, token = my_token1)
  currentFeed <- currentFeed[-c(1,6:10,13:90)]
  allCurrentInfo <- right_join(currentFeed, TLsV2, by = "screen_name") %>% 
    na.omit(text) 
  allCurrentInfo<- allCurrentInfo[-c(7,8,10)]  
  allCurrentInfo <- allCurrentInfo[which(allCurrentInfo$is_quote == F),] ## get rid of quotes and retweets
  allCurrentInfo <- allCurrentInfo[which(allCurrentInfo$is_retweet == F),]
  allCurrentInfo <- allCurrentInfo[-c(5,6)]
  allCurrentInfo <- unique.data.frame(allCurrentInfo)
  currentOutput <- rbind(currentOutput, allCurrentInfo)
  cat ("Completed", i,  TLsV2$Handle[i], ";", dim(allCurrentInfo)[1], "added", "total :", dim(currentOutput)[1], "\n")
}
{
CH_TML <- currentOutput
CH_TML <- separate(CH_TML, created_at, c("Date", "Time"), sep= " ")
CH_TML <- separate(CH_TML, Date, c("YYYY", "MM", "DD"), sep= "-")
CH_TML <- separate(CH_TML, Time, c("hh", "mm", "ss"), sep= ":")

CH_TML <- CH_TML[which(CH_TML$YYYY == thisYear), ]
CH_TML <- CH_TML[which(CH_TML$MM == YesterdayMonth), ]
CH_TML <- CH_TML[which(CH_TML$DD == YesterDate), ]
CH_TML <- unique.data.frame(CH_TML)
write.csv(CH_TML, paste(DailyPath, "-CH_TML.csv", sep=""))
#write.csv(BE_TML, paste("/R/NewsTMLS/", YesterdayYMDString, "-CH_TML.csv", sep=""))


}
}
{
currentOutput <- data.frame() ## change to 54:93
for (i in 95:105){
  currentFeed <- get_timeline(TLsV2$Handle[95], n = 1000, token = my_token1)
  currentFeed <- currentFeed[-c(1,6:10,13:90)]
  allCurrentInfo <- right_join(currentFeed, TLsV2, by = "screen_name") %>% 
    na.omit(text) 
  allCurrentInfo<- allCurrentInfo[-c(7,8,10,10)]  
  allCurrentInfo <- allCurrentInfo[which(allCurrentInfo$is_quote == F),] ## get rid of quotes and retweets
  allCurrentInfo <- allCurrentInfo[which(allCurrentInfo$is_retweet == F),]
  allCurrentInfo <- allCurrentInfo[-c(5,6)]
  allCurrentInfo <- unique.data.frame(allCurrentInfo)
  currentOutput <- rbind(currentOutput, allCurrentInfo)
  cat ("Completed", i, TLsV2$Handle[i], "+", dim(allCurrentInfo)[1], "->", dim(currentOutput)[1], "\n")
}
}
{## change to 95:161
for (i in 106:161){
currentFeed <- get_timeline(TLsV2$Handle[i], n = 1000, token = my_token1)
currentFeed <- currentFeed[-c(1,6:10,13:90)]
allCurrentInfo <- right_join(currentFeed, TLsV2, by = "screen_name") %>% 
    na.omit(text) 
  allCurrentInfo<- allCurrentInfo[-c(7,8,10)]  
  allCurrentInfo <- allCurrentInfo[which(allCurrentInfo$is_quote == F),] ## get rid of quotes and retweets
  allCurrentInfo <- allCurrentInfo[which(allCurrentInfo$is_retweet == F),]
  allCurrentInfo <- allCurrentInfo[-c(5,6)]
  allCurrentInfo <- unique.data.frame(allCurrentInfo)
  currentOutput <- rbind(currentOutput, allCurrentInfo)
  cat ("Completed", i,  TLsV2$Handle[i], ";", dim(allCurrentInfo)[1], "added", "total :", dim(currentOutput)[1], "\n")
}
}
{
FR_TML <- currentOutput
FR_TML <- separate(FR_TML, created_at, c("Date", "Time"), sep= " ")
FR_TML <- separate(FR_TML, Date, c("YYYY", "MM", "DD"), sep= "-")
FR_TML <- separate(FR_TML, Time, c("hh", "mm", "ss"), sep= ":")

FR_TML <- FR_TML[which(FR_TML$YYYY == thisYear), ]
FR_TML <- FR_TML[which(FR_TML$MM == YesterdayMonth), ]
FR_TML <- FR_TML[which(FR_TML$DD == YesterDate), ]

FR_TML <- unique.data.frame(FR_TML)
write.csv(FR_TML, paste(DailyPath, "-FR_TML.csv", sep=""))
#write.csv(BE_TML, paste("/R/NewsTMLS/", YesterdayYMDString, "-FR_TML.csv", sep=""))

}
{
currentOutput <- data.frame()
for (i in 162:dim(TLsV2)[1]){
currentFeed <- get_timeline(TLsV2$Handle[i], n = 1000, token = my_token1)
currentFeed <- currentFeed[-c(1,6:10,13:90)]
allCurrentInfo <- right_join(currentFeed, TLsV2, by = "screen_name") %>% 
    na.omit(text) 
allCurrentInfo<- allCurrentInfo[-c(7,8,10)]  
allCurrentInfo <- allCurrentInfo[which(allCurrentInfo$is_quote == F),] ## get rid of quotes and retweets
allCurrentInfo <- allCurrentInfo[which(allCurrentInfo$is_retweet == F),]
allCurrentInfo <- allCurrentInfo[-c(5,6)]
allCurrentInfo <- unique.data.frame(allCurrentInfo)
currentOutput <- rbind(currentOutput, allCurrentInfo)
cat ("Completed", i,  TLsV2$Handle[i], ";", dim(allCurrentInfo)[1], "added", "total :", dim(currentOutput)[1], "\n")
}  
}
{
LX_TML <- currentOutput
LX_TML <- separate(LX_TML, created_at, c("Date", "Time"), sep= " ")
LX_TML <- separate(LX_TML, Date, c("YYYY", "MM", "DD"), sep= "-")
LX_TML <- separate(LX_TML, Time, c("hh", "mm", "ss"), sep= ":")

LX_TML <- LX_TML[which(LX_TML$YYYY == thisYear), ]
LX_TML <- LX_TML[which(LX_TML$MM == YesterdayMonth), ]
LX_TML <- LX_TML[which(LX_TML$DD == YesterDate), ]
LX_TML <- unique.data.frame(LX_TML)

#write.csv(BE_TML, paste("/R/NewsTMLS/", YesterdayYMDString, "-LX_TML.csv", sep=""))
write.csv(LX_TML, paste(DailyPath, "-LX_TML.csv", sep=""))
}

outputPathLevel1 <- paste("/R/NewsTMLS/IndividualsN/", thisYear, "/", sep="")
#outputPathLevel1 <- paste("/R/NewsTMLS/Archive/IndividualsN/", thisYear, "/", sep="")
outputPathLevel2 <- paste(outputPathLevel1, thisYear,  "-", YesterdayMonth, "/", sep="")
outputPathLevel3 <- paste(outputPathLevel2, thisYear,  "-", YesterdayMonth, "-", YesterDate, "/", sep="")
ifelse( !dir.exists(file.path(outputPathLevel1)),   dir.create(file.path(outputPathLevel1)),   FALSE  )
ifelse( !dir.exists(file.path(outputPathLevel2)),   dir.create(file.path(outputPathLevel2)),   FALSE  )
ifelse( !dir.exists(file.path(outputPathLevel3)),   dir.create(file.path(outputPathLevel3)),   FALSE  )

currentSelection <- rbind(BE_TML, CA_TML, CH_TML, FR_TML, LX_TML)
currentSelection$text <- gsub("http.+", "", currentSelection$text)
currentSelection$text <- gsub("#.+? ", "", currentSelection$text)
currentSelection$text <- gsub("@.+? ", "", currentSelection$text)
currentSelection$text <-   gsub("\'|’", "\' ", currentSelection$text) ## space elisions
currentSelection$text <-   gsub("  ", " ", currentSelection$text) ## remove double spaces
currentSelection$text <-   gsub("_", "", currentSelection$text) ## remove double spaces
currentSelection$text <-   gsub("-|–", "-", currentSelection$text) ## remove double spaces
currentSelection$text <-   gsub("[\"“‘«]", "\"", currentSelection$text) # reokace opening quote variations with std double "
currentSelection$text <-   gsub("[”’»]", "\"", currentSelection$text) # idem for closing
currentSelection$text <- gsub("[0-9]+", "", currentSelection$text)
currentSelection$text <- gsub(",", "", currentSelection$text)
currentSelection$text <- gsub("\\.", "", currentSelection$text)
currentSelection$text <- gsub("tco.*ing.", "", currentSelection$text)

for (i in 1:dim(currentSelection)[1]){
currentTweetContent <- currentSelection$text[i]
currrentTweetID <- currentSelection$status_id[i]
FullName <- paste(outputPathLevel3, currrentTweetID, ".txt", sep="")
writeChar(currentTweetContent, FullName)
}
beep(2)
targetMM <- "09"
```

 ```{r}
# write.csv(FR_TML, paste(DailyPath, "-FR_TML.csv", sep=""))
# write.csv(BE_TML, paste(DailyPath, "BE_TML.csv", sep=""))
# write.csv(CA_TML, paste(DailyPath, "-CA_TML.csv", sep=""))
# write.csv(CH_TML, paste(DailyPath, "-CH_TML.csv", sep=""))
# write.csv(LX_TML, paste(DailyPath, "-LX_TML.csv", sep=""))
# 
# writeChar (as.character(FR_TML), paste("R/NewsTMLS/A", YesterdayYMDString, "-FR_TML.csv", sep=""))
# 
# write.csv(BE_TML, paste("/R/NewsTMLS/A", YesterdayYMDString, "-BE_TML.csv", sep=""))
# 
# write.csv(CA_TML, paste("/R/NewsTMLS/A", YesterdayYMDString, "-CA_TML.csv", sep=""))
# 
# write.csv(CH_TML, paste("/R/NewsTMLS/A", YesterdayYMDString, "-CH_TML.csv", sep=""))
# 
# write.csv(LX_TML, paste("/R/NewsTMLS/A", YesterdayYMDString, "-LX_TML.csv", sep=""))

```


## ERROR RECOVERY - LOAD FROM DAILY csv


## Get 
```{r}

# ArchivePath <- "R/NewsTMLS/Archive/Dailies/"
# TargetYYYY <- "2021"
# TargetMM <- "08"
# TargetDD <- "11"
# ######## note need to check number of columns in archive (1,9 potentially)
# currentOutputBE <- read.csv(paste(ArchivePath, "/", TargetYYYY, "/", TargetYYYY, "-", TargetMM, "-", TargetDD, "-BE_TML.csv", sep="" ), colClasses = c("status_id" = "character"))
# currentOutputBE <- currentOutputBE[-c(1,9)]
# 
# currentOutputCA <- read.csv(paste(ArchivePath, "/", TargetYYYY, "/", TargetYYYY, "-", TargetMM, "-", TargetDD, "-CA_TML.csv", sep="" ), colClasses = c("status_id" = "character"))
# currentOutputCA <- currentOutputCA[-c(1)]
# 
# currentOutputCH <- read.csv(paste(ArchivePath, "/", TargetYYYY, "/", TargetYYYY, "-", TargetMM, "-", TargetDD, "-CH_TML.csv", sep="" ), colClasses = c("status_id" = "character"))
# currentOutputCH <- currentOutputCH[-c(1)]
#   
# currentOutputFR <- read.csv(paste(ArchivePath, "/", TargetYYYY, "/", TargetYYYY, "-", TargetMM, "-", TargetDD, "-FR_TML.csv", sep="" ), colClasses = c("status_id" = "character"))
# currentOutputFR <- currentOutputFR[-c(1)]
# 
# currentOutputLX <- read.csv(paste(ArchivePath, "/", TargetYYYY, "/", TargetYYYY, "-", TargetMM, "-", TargetDD, "-LX_TML.csv", sep="" ), colClasses = c("status_id" = "character"))
# currentOutputLX <- currentOutputLX[-c(1)]
# 
# 
# {
# # Filtering formula uf needed
# # currentOutputLX <- currentOutputLX
# # currentOutputLX <- currentOutputLX[which(currentOutputLX$Pays == "LX"), ]
# # 
# }
# 
# outputPathLevel1 <- paste("/R/NewsTMLS/Archive/IndividualsN/", TargetYYYY, "/", sep="")
# outputPathLevel2 <- paste(outputPathLevel1, TargetYYYY,  "-", TargetMM, "/", sep="")
# outputPathLevel3 <- paste(outputPathLevel2, TargetYYYY,  "-", TargetMM, "-", TargetDD, "/", sep="")
# ifelse( !dir.exists(file.path(outputPathLevel1)),   dir.create(file.path(outputPathLevel1)),   FALSE  )
# ifelse( !dir.exists(file.path(outputPathLevel2)),   dir.create(file.path(outputPathLevel2)),   FALSE  )
# ifelse( !dir.exists(file.path(outputPathLevel3)),   dir.create(file.path(outputPathLevel3)),   FALSE  )
# 
# currentSelection <- rbind(currentOutputBE, currentOutputCA, currentOutputCH, currentOutputFR, currentOutputLX)
# currentSelection$text <- gsub("http.+", "", currentSelection$text)
# currentSelection$text <- gsub("#.+? ", "", currentSelection$text)
# currentSelection$text <- gsub("@.+? ", "", currentSelection$text)
# currentSelection$text <-   gsub("\'|’", "\' ", currentSelection$text) ## space elisions
# currentSelection$text <-   gsub("  ", " ", currentSelection$text) ## remove double spaces
# currentSelection$text <-   gsub("_", "", currentSelection$text) ## remove double spaces
# currentSelection$text <-   gsub("-|–", "-", currentSelection$text) ## remove double spaces
# currentSelection$text <-   gsub("[\"“‘«]", "\"", currentSelection$text) # reokace opening quote variations with std double "
# currentSelection$text <-   gsub("[”’»]", "\"", currentSelection$text) # idem for closing
# currentSelection$text <- gsub("[0-9]+", "", currentSelection$text)
# currentSelection$text <- gsub(",", "", currentSelection$text)
# currentSelection$text <- gsub("\\.", "", currentSelection$text)
# currentSelection$text <- gsub("tco.*ing.", "", currentSelection$text)
# 
# for (i in 1:dim(currentSelection)[1]){
# currentTweetContent <- currentSelection$text[i]
# currrentTweetID <- currentSelection$status_id[i]
# FullName <- paste(outputPathLevel3, currrentTweetID, ".txt", sep="")
# writeChar(currentTweetContent, FullName)
# }

```



# write.csv(FR_TML, paste(DailyPath, "-FR_TML.csv", sep=""))
# write.csv(BE_TML, paste(DailyPath, "BE_TML.csv", sep=""))
# write.csv(CA_TML, paste(DailyPath, "-CA_TML.csv", sep=""))
# write.csv(CH_TML, paste(DailyPath, "-CH_TML.csv", sep=""))
# write.csv(LX_TML, paste(DailyPath, "-LX_TML.csv", sep=""))
# writeChar (as.character(FR_TML), paste("/R/NewsTMLS/A", YesterdayYMDString, "-FR_TML.csv", sep=""))
# write.csv(BE_TML, paste("/R/NewsTMLS/A", YesterdayYMDString, "-BE_TML.csv", sep=""))
# write.csv(CA_TML, paste("/R/NewsTMLS/A", YesterdayYMDString, "-CA_TML.csv", sep=""))
# write.csv(CH_TML, paste("/R/NewsTMLS/A", YesterdayYMDString, "-CH_TML.csv", sep=""))
# write.csv(LX_TML, paste("/R/NewsTMLS/A", YesterdayYMDString, "-LX_TML.csv", sep=""))

